\documentclass[kul]{kulakarticle} % options: kulak (default) or kul

% die proffen zijn de grootste mongolen van de kul die ze ne cursus hebben laten maken en de volledige vrijheid hebben gegeven om ons leven zuur te maken

\usepackage[english]{babel}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{siunitx}
\sisetup{
	per-mode = symbol
}
\hypersetup{
	linktoc=all, %set to all if you want both sections and subsections linked
}
\hypersetup{
	pdftitle={Global Challenges for a Sustainable Society},
	pdfsubject={If I Had More Time, I Would Have Written a Shorter Letter},
	pdfauthor={Kobe Michiels, Wout Lyen, Robbe Decapmaker},
	colorlinks=true, %Colours links instead of ugly boxes
	linkcolor=black,
	urlcolor=cyan
}
\setcounter{secnumdepth}{4}

\title{Global Challenges for a Sustainable Society}
\author{Kobe Michiels, Wout Lyen, Robbe Decapmaker}
\date{Academic Year 2023 -- 2024}
\address{
	\textbf{Campus Group T} \\
	Bachelor of Engineering Technology \\
	Engineering and Sustainability: Philosophy and Global Challenges}

\begin{document}

\maketitle

\section*{Summary}

This is a summary of the Massive Open Online Course (MOOC) \href{https://www.edx.org/learn/science/ku-leuven-global-challenges-for-a-sustainable-society?webview=false&campaign=Global+Challenges+for+a+Sustainable+Society&source=edx&product_category=course&placement_url=https%3A%2F%2Fwww.edx.org%2Fschool%2Fkuleuvenx}{KULeuvenX: Global Challenges for a Sustainable Society}, based on the provided study guides part of the \href{https://onderwijsaanbod.kuleuven.be/syllabi/v/e/T3AID1E.htm#activetab=inhoud_idp1690064}{Engineering and Sustainability: Philosophy and Global Challenges} course of the Bachelor of Engineering Technology at KU Leuven.

\section*{Contributors}
\href{https://github.com/michielskobe}{Kobe Michiels}\\
\href{https://github.com/woutlyen}{Wout Lyen}\\
\href{https://github.com/debber1}{Robbe Decapmaker}

\section*{Disclaimer}
The summary provided herein is a user-generated content based on the previously mentioned MOOC offered by KU Leuven. The original content, including but not limited to text, images, audio, and video materials, is the intellectual property of KU Leuven and is protected by copyright law.
\\\\
This course may also include images sourced from third parties that are subject to their respective copyrights. The use of such images in the original course is based on licenses, permissions, or fair use principles as determined by KU Leuven.
\\\\
This summary is intended for personal use only and is not meant for distribution, reproduction, or any form of commercial use. The user acknowledges that any unauthorized use of the original course content may infringe upon the intellectual property rights of KU Leuven or the respective copyright owners.
\\\\
The summary is a condensed representation of the key concepts covered in the course and may not capture the full depth and nuance of the original content. Users are encouraged to enroll in the official course offered by KU Leuven to access the complete and unaltered educational materials for a comprehensive understanding.
\\\\
The contributors asserts that this summary is provided in good faith for informational purposes and is not a substitute for the official course. The contributors disclaim any liability for the accuracy, completeness, or reliability of the summary and shall not be held responsible for the academic outcomes or any other consequences arising from its use. The contributors also refrain from answering any questions about this summary or its contents.
\newpage

\newpage
\setcounter{tocdepth}{2}
\tableofcontents
\newpage
\subfile{chapters/climate}
\newpage
\subfile{chapters/biodiversity}
\newpage
\subfile{chapters/demography}
\newpage
\subfile{chapters/energy}
\newpage
\subfile{chapters/raw_materials_and_circular_economy}
\newpage
\subfile{chapters/food_security}
\newpage
\subfile{chapters/migration}
\newpage
\subfile{chapters/buildings}
\newpage
\subfile{chapters/mobility}
\newpage
\subfile{chapters/economics_for_sustainability}
\newpage
\subfile{chapters/social_and_economic_inequality}
\newpage
\subfile{chapters/human_behaviour}
\newpage
\subfile{chapters/global_governance}

\end{document}
